Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-09-04 Ben_Manuscripts/stochastic_transport/Outline.tex
updated outline.
Nailing down transport models + documenting them

%MRS: better to have the first outline shorter to iterate more quickly!
%BJC1: right, this one has been in the works for a while now. Wrote the anomalous diffusion methods a long time ago

%MRS: better to have a title that described a finding, rather than the
%approach used.  But we may need to wait a bit further until we can decide on a finding.
%MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
%BJC1: Yea maybe Chris as an acknowledgement on this one. He didn't directly contribute anything other than pointing
%me towards Greg Morrin who pointed me towards useful anomalous diffusion literature.
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \section{Introduction}
  %BJC: obviously this section will get beefed up
  We need highly selective membranes in order to perform efficient separations. \\

@@

  Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
  into mechanically strong membranes.
  \begin{itemize}
  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
	sized pores and have the potential to disrupt conventional membrane separation
	techniques by being selective based not only on size and charge, but on chemical
	functionality as well.
	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
	pores. They are easier to make.
  \end{itemize}

@@

@@

  \noindent We can use the observations of transport from our previous work in order to create 
  state-based models.
  \begin{itemize}
  	\item We know that dynamics differ between solutes moving inside the pores and 
  	in the tails.
  	\item We can use the anomalous diffusion approach to model to our data as a 
  	function of radial distance from the closest pore center.
  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
  	methods of Markov state modeling.
  \end{itemize}

@@

@@

  Our first approach is based on the anomalous diffusion literature, applying the 
  mathematical formalism describing subdiffusive transport to observed solute 
  trajectories.
  \begin{itemize}
    \item We determine the most likely subdiffusive mechanisms at play using the 
    flow chart in figure X. 
    \item We then fit anomalous diffusion models in two ways: First, based on a
    single set of parameters. Second, we use a two-state approach incorporating
    two sets of parameters based on a solute's radial distance from the pore center. 
  \end{itemize}

  The second approach adapts the MSM framework to a relatively small set of known 
  states based on the three observed solute trapping mechanisms.
  \begin{itemize}
    \item We extend the framework to include dynamics between jumps. 
    \item That is we incorporate the magnitude and temporal dependence of the 
    time series fluctuations between each transition to a different state. 
    \item Temporal dependence has a significant influence on mean squared displacement.
  \end{itemize}

@@

  % MRS: you intend this to be a separate model than the above?  If so, make clearer.
  % BJC1: renamed, is that what you meant?
  \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}

@@

  % BJC1: not sure about this anymore. Might eventually change to Levy. But in the 
  % interest of simplicity, maybe leave it at Gaussian.
  For solutes in our system, the distribution of hop lengths appears to be
  well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
  metzler_anomalous_2014,neusius_subdiffusion_2009}  % Note that this is different from the distribution of all increments (which is heavy-tailed)
  \begin{itemize}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
  \end{itemize}

  \noindent The distribution of dwell times is expected to fit a power law
  distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  \begin{itemize}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
  \end{itemize}

@@

  \subsection{Markov State Models}\label{method:MSMs}

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. 
  \begin{itemize}
  	\item Therefore, there is no need to subject our trajectories to any reduction
  	in dimensionality. 
  	\item However, we will adopt the validation techniques used in the packages
  	mentioned above.  
  	%BJC: not sure the best way to lay these out
  	\item The states we've chosen include all combinations of trapping mechanisms 
  	in the pore and out of the pore:
    \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ll}
	  \hline
	  1. In tails                                  & 5. In pores                                  \\
	  2. In tails and hydrogen bonding             & 6. In pores and hydrogen bonding             \\
	  3. In tails and associated with sodium       & 7. In pores and associated with sodium       \\
	  4. In tails, hydrogen bonding and associated & 8. In pores, hydrogen bonding and associated \\
	  \hline
	  \end{tabular}
	  \caption{}\label{table:water_content}
   \end{table}
%  	\begin{enumerate}
%  	  \item Trapped in tails
%  	  \item Trapped in tails and hydrogen bonding
%  	  \item Trapped in tails and associated with sodium
%  	  \item Trapped in tails, hydrogen bonding and associated
%  	  \item In pores
%  	  \item In pores and hydrogen bonding
%  	  \item In pores and associated with sodium
%  	  \item In pores, hydrogen bonding and associated
%  	\end{enumerate}
  	\item These choices assume that there are no significant kinetic effects resulting
  	from solute conformational changes or pore size fluctuations, an assumption 
  	that may be relaxed in future work.
  \end{itemize}

@@

  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
  \begin{itemize}
    \item For independent and identically distributed (iid) random variables, the 
    generalized central limit theorem guarantees convergence of the associated 
    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%    sample size, the generalized central limit theorem guarantees the convergence of
%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
    \item The characteristic equation describing the Fourier transform of a L\'evy 
    stable PDF is given below:
    \begin{equation}
    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
    \end{equation}
    \item Where $\omega$ is defined with something that is complicated to format and can be 
    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
    functions, is the Gaussian PDF ($\alpha$ = 2).
    \item The more general family of L\'evy stable distributions allows
    greater flexibility in defining the observed emission distribution PDFs.
    \item In the case that the empirical emission distributions are iid, sequential draws
    from a L\'evy stable PDF defines a L\'evy process. 
    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
    probability distributions if we instead consider the dynamics to be governed by a
    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
    \item OU processes contain temporal dependence but the marginal observation distributions
    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
    \item We will discuss the implications of each.  
    % MRS: does the process described above include the motion within the state? That is something I feel that the
    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
    % are adding to the standard MSM.
  \end{itemize}

@@

  %BJC: need to add some validation of Markovian behavior and time step choice.

@@

  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode models 
  (see Table~\ref{table:sfbm_params}).
  \begin{itemize}
    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values . 
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the MSD.
  \end{itemize}

@@

  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
  MSDs.
  \begin{itemize}
	\item We simulated 10000 sFBM trajectories of the same length as our MD
	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
	\item The final MSDs of the sFBM trajectories are compared to those 
	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
	\item We would like to emphasize that we rely on the MD MSD values in order to
	define trends in the total MSD, while the sFBM trajectories and parameter 
	values allow us to speculate as to the reasons for the observed trends. 
	\item There is a non-negligible amount of error in the calculation of 
	each parameter which prevents us from reliably portraying our sFBM MSDs as
	reduced	uncertainty MD MSDs.
	% BJC: I think it's more the power law tails that increases uncertainty.
  \end{itemize}

  % BJC1: yea we'll see
  The two-mode sFBM model does a better job than the one-mode model at 
  reproducing the MD MSD trends. 
  \begin{itemize}
    \item One-mode model generally undershoots MSDs.
  \end{itemize}

  %BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, one-mode sfbm MSD, two-mode sfbm MSD
  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{all_emsds.pdf}
  \caption{}\label{fig:all_msds}
  \end{figure}

  \subsection{Markov State Model Fits}\label{section:msm_results}

  The emission distributions are non-Gaussian and heavy-tailed (see Figure~\ref{fig:emissions_MET}).
  \begin{itemize}
    \item The heavy tails of the distribution are a consequence of hopping.
    \item Heavily sampled states fit well to L\'evy stable distributions.
    \item The rarer states have less data, but we still assume L\'evy stable distributions.
  \end{itemize}

@@

  % BJC: need better or more descriptive way of describing stochastic simulations
  % BJC: or could say that whenever we say simulations, we mean stochastic simulations unless it is specified as a molecular dynamics simulation.
  % MRS: could say timeseries simulation?  MD is stochastic as well.
  Simulating solute trajectories (see Section~\ref{method:MSMs}) by drawing independent  
  observations from the emission distributions yields near linear MSD curves
  with final values that are far higher than those observed in our molecular simulations.
  \begin{itemize}
	% BJC: right number of solute trajectories to simulate for comparison? More tightens the error bars
    \item In the case of methanol, the final MSD value is about 25x higher than that observed in our
    previous transport study (see Figure~\ref{fig:msd_MET}).
    \item The linear behavior of the MSD curve is not consistent with subdiffusion.
  \end{itemize}
  %MRS: so, is there a way we should have been able to tell beforrehand that this approach didn't work that we an explain?
  %or can we show we needed to do this to get the results?
  %BJC1: could just show autocorrelation function of all increments, which has negative dip at k=1 
  \begin{figure}[!h]
  \centering
  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
  \caption{}\label{fig:msd_MET}
  \end{figure}

  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
  \begin{itemize}
    \item In general, we observe negative correlation between hops.
    \item A L\'evy driven OU process may be a more appropriate way to model
    the stochastic dynamics of this system since you can incorporate autocorrelation.
    \item Extracting reliable correlation functions is difficult with our data
    due to relatively frequent switching resulting in sets of short disjoint time 
    series describing each state.
    % \item Therefore we did not do this and attempted to fit a different model. 
    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
  \end{itemize}

@@

  We have tested two different mathematical frameworks for describing solute
  motion in an H\textsubscript{II} phase LLC membrane.
  \begin{itemize}
    \item Markov state modeling with predefined states gives a nice description
    of transitions between observed states as well as the type of stochastic 
    behavior shown in each state. However, it doesn't accurately portray correlated
    time series behavior leading to overpredicted MSDs.
    \item Subordinated fractional Brownian motion has a nice theoretical foundation
    in the anomalous diffusion literature. A two mode model that describes dynamics
    based on whether a solute is in or out of the pore region leads to MSDs fairly
    consistent with MD simulated trajectories.
  \end{itemize}

>>>>

%MRS: better to have a title that described a finding, rather than the
%approach used.  But we may need to wait a bit further until we can decide on a finding.
%MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
\title{Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
%BJC1: Yea maybe Chris as an acknowledgement on this one. He didn't directly contribute anything other than pointing
%me towards Greg Morrin who pointed me towards useful anomalous diffusion literature.
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \section{Introduction}

  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?  Let people know right from the start what the paper is about.  This paragraph should still be in the intro, but start with something that captures the main question of the paper. 
  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles.
  \begin{itemize}
    \item The complexity of a model generally parallels the complexity of the 
    transport mechanism at hand, as well as the desired outputs.
    \item In dense homogeneous membranes, the solution-diffusion model can extract
    diffusion and partition coefficients and has successfully predicted solute transport
    rates.
    \item Analogously, pore-flow models yield predictions of diffusion coefficients
    and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
    \item Single particle tracking allows us to further characterize more complex
    diffusive behavior.
    \item Finally, Molecular simulation provides a framework for studying both single
    particle dynamics and bulk transport properties with atomic resolution.
    \item All of these approaches facilitate speculation on the molecular origins of
    separations and suggest experiments that should be run by attempting to give a more
    intuitive understanding of how solutes move as a function of their environment.
%    \item The hydrodynamic Ferry model is the simplest pore-flow model, with extensions such
%    as the Donnan-Steric Pore Model which includes extra terms for the pressure gradient
%    across the membrane and membrane charge.
%    \item Dischinger et al. created an empirical correlation to determine the
%    effect of solute physicochemical properties on solute rejection.
  \end{itemize}

%  \begin{itemize}
%    \item More recently, rapid advancements in computational power have made it feasible
%    to observe transport in simulated systems with atomic resolution. This allows us to
%    shift towards analysis of the motion of individual particles and gives an even more 
%    fundamental understanding of observed bulk properties.
%  \end{itemize}

  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  We need highly selective membranes in order to perform efficient separations. \\

@@

  Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
  into mechanically strong and highly selective membranes.
  \begin{itemize}
  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
	sized pores and have the potential to disrupt conventional membrane separation
	techniques by being selective based not only on size and charge, but on chemical
	functionality as well.
	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
	pores. They are easier to make.
  \end{itemize}

@@

  % BJC2: moved this from below
  Our first modeling approach is based on the anomalous diffusion literature, applying the 
  mathematical formalism describing subdiffusive transport to observed solute 
  trajectories.
  \begin{itemize}
    \item We determine the most likely subdiffusive mechanisms at play using the 
    flow chart in figure X. 
    \item We then fit anomalous diffusion models in two ways: First, based on a
    single set of parameters. Second, we use a two-state approach incorporating
    two sets of parameters based on a solute's radial distance from the pore center. 
  \end{itemize}

@@

  \noindent We can use the observations of transport from our previous work in order to create 
  state-based models.
  \begin{itemize}
  	\item We know that dynamics differ between solutes moving inside the pores and 
  	in the tails.
  	\item We can use the anomalous diffusion approach to model our data as a 
  	function of radial distance from the closest pore center.
  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
  	methods of Markov state modeling.
  \end{itemize}

@@

  %MRS1: probably want to make clear that you really are doing some
  %substantially different things in in MSM modeling than most people
  %do, by adding on modeling the z-diffusion as an auxiliary variable
  %of the state.  I think that's actually kind of innovative.

  %BJC2: moved this paragraph up from below to clarify novelty of this approach
  Our second modeling approach adapts the MSM framework to a relatively small set
  of known states based on the three observed solute trapping mechanisms.
  \begin{itemize}
    \item Standard MSMs assume first order kinetics and are typically applied 
    towards determining equilibrium populations of various state configurations.
    \item We extend the framework to include dynamics within states and
    between jumps. 
    \item That is we incorporate the magnitude and temporal dependence of the 
    time series fluctuations between each transition to a different state. 
    \item Temporal dependence has a significant influence on mean squared displacement.
  \end{itemize}

@@

@@

  \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}

@@

  % BJC1: not sure about this anymore. Might eventually change to Levy. But in the 
  % interest of simplicity, maybe leave it at Gaussian.
  % BJC2: This will change to Levy. 
  For solutes in our system, the distribution of hop lengths appears to be
  well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
  metzler_anomalous_2014,neusius_subdiffusion_2009}  % Note that this is different from the distribution of all increments (which is heavy-tailed)
  \begin{itemize}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
  \end{itemize}

  \noindent The distribution of dwell times is expected to fit a power law
  distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  \begin{itemize}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
        %MRS1: can just say bootstrapping.
  \end{itemize}

@@

  \subsection{Markov State Models}\label{method:MSMs}  
  % BJC2: still need a better name
  % name candidates - correlated MSMs, Dynamical mode switching

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. 
  \begin{itemize}
  	\item Therefore, there is no need to subject our trajectories to any reduction
  	in dimensionality. 
  	\item However, we will adopt the validation techniques used in the packages
  	mentioned above.  
  	%BJC: not sure the best way to lay these out
  	\item The states we've chosen include all combinations of trapping mechanisms 
  	in the pore and out of the pore:
        %MRS: ``1. in tails and 5. in pores seem to encompass the things below them. Maybe us ``in tails, not trapped,'' etc. as the last entry in each column.'' 
        %BJC2: good point
    \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ll}
	  \hline
	  1. In tails, not trapped                     & 5. In pores, not trapped                     \\
	  2. In tails and hydrogen bonding             & 6. In pores and hydrogen bonding             \\
	  3. In tails and associated with sodium       & 7. In pores and associated with sodium       \\
	  4. In tails, hydrogen bonding and associated & 8. In pores, hydrogen bonding and associated \\
	  \hline
	  \end{tabular}
	  \caption{}\label{table:water_content}
   \end{table}
%  	\begin{enumerate}
%  	  \item Trapped in tails
%  	  \item Trapped in tails and hydrogen bonding
%  	  \item Trapped in tails and associated with sodium
%  	  \item Trapped in tails, hydrogen bonding and associated
%  	  \item In pores
%  	  \item In pores and hydrogen bonding
%  	  \item In pores and associated with sodium
%  	  \item In pores, hydrogen bonding and associated
%  	\end{enumerate}
  	\item These choices assume that there are no significant kinetic effects resulting
  	from solute conformational changes or pore size fluctuations, an assumption 
  	that may be relaxed in future work.
  \end{itemize}

@@

  % BJC2: An abbreviated from of this paragraph probably belongs in previous section
  % since I'll be using subordinated levy motion.
  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
  \begin{itemize}
    \item For independent and identically distributed (iid) random variables, the 
    generalized central limit theorem guarantees convergence of the associated 
    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%    sample size, the generalized central limit theorem guarantees the convergence of
%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
    \item The characteristic equation describing the Fourier transform of a L\'evy 
    stable PDF is given below:
    \begin{equation}
    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
    \end{equation}
    \item Where $\omega$ is defined with something that is complicated to format and can be 
    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
    functions, is the Gaussian PDF ($\alpha$ = 2).
    \item The more general family of L\'evy stable distributions allows
    greater flexibility in defining the observed emission distribution PDFs.
    \item In the case that the empirical emission distributions are iid, sequential draws
    from a L\'evy stable PDF defines a L\'evy process. 
    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
    probability distributions if we instead consider the dynamics to be governed by a
    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
    %MRS1: you many consider putting some of the long explanations in supporrting. 
    \item OU processes contain temporal dependence but the marginal observation distributions
    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
    \item We will discuss the implications of each.  
    % MRS: does the process described above include the motion within the state? That is something I feel that the
    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
    % are adding to the standard MSM.
  \end{itemize}

@@

  % BJC: need to add some validation of Markovian behavior and time step choice.

@@

  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
  of $\sigma$, $\alpha$, $H$ and $\lambda$ for each solute for the 1 and 2 mode models 
  (see Table~\ref{table:sfbm_params}).
  \begin{itemize}
    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values. 
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Higher values of $\lambda$ truncates the power law distribution earlier
  	preventing extremely long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the MSD.
  \end{itemize}

@@

  % BJC2: Adding all combinations of distributions.
  % Power law + Gaussian, Power law + Levy, Power law w/cutoff + Gaussian, Power Law w/cutoff + Levy
  % BJC2: Probably a good idea to at least mention results when no anitcorrelation is included
  \noindent We compared the MSD of simulated sFBM and sFLM trajectories to MD simulated
  MSDs.
  \begin{itemize}
	\item We simulated 10000 sFBM trajectories of the same length as our MD
	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
	\item The final MSDs of the sFBM trajectories are compared to those 
	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
	\item We would like to emphasize that we rely on the MD MSD values in order to
	define trends in the total MSD, while the sFBM trajectories and parameter 
	values allow us to speculate as to the reasons for the observed trends. 
%	\item There is a non-negligible amount of error in the calculation of 
%	each parameter which prevents us from reliably portraying our sFBM MSDs as
%	reduced	uncertainty MD MSDs.
	% BJC: I think it's more the power law tails that increases uncertainty.
	% BJC2: Error looks relatively small now.
  \end{itemize}

  % BJC2: A qualitative comparison of sFLM trajectories to MD trajectories might be nice.

  \noindent The power law with exponential cut-off has the largest effect on the on 
  the match between MD MSD and sFLM trajectories.
  \begin{itemize}
    \item Using the power law with cutoff produces predictions in relatively good agreement
    with MD.
  \end{itemize}

  \noindent The choice between Levy and Gaussian distributions has only a small effect, 
  but the Levy appears to fit emission distributions better.

  % BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, 
  % one-mode sfbm MSD, two-mode sfbm MSD.
  % BJC2: Actually I think I prefer showing the MSD curves on one plot, like in my research journal. Since it shows shape.
  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{all_emsds.pdf}
  \caption{}\label{fig:all_msds}
  \end{figure}

  \noindent We can use the model to project our simulations out to very long timescales.
  \begin{itemize}
    \item We can not definitively say which combination of distributions are best to use.
    \item Although the longest observed dwell times and hop lengths are less than
    the length of the simulated trajectories and box lengths respectively, it is still possible
    that that extremely long dwell times and hops are observed experimentally in rare but
    significant cases.
    \item We present long timescale projections using combinations of each distribution in the
    table below
  \end{itemize}

  % BJC2: table of long timescale projections using combinations of dwell and hop distributions. 
  %% TABLE %%

  \subsection{Markov State Model Fits}\label{section:msm_results}
  % BJC2: This section should parallel the previous section in terms of presentation of results.

  We constructed emission distributions which correspond to each entry in the transition
  matrix.
  \begin{itemize}
    \item Some states are sampled far more frequently than other leading to better converged
    distributions.
  \end{itemize}

  The emission distributions are non-Gaussian and heavy-tailed (see Figure~\ref{fig:emissions_MET}).
  \begin{itemize}
    %\item The heavy tails of the distribution are a consequence of hopping.
    \item Heavily sampled states fit well to L\'evy stable distributions.
    \item The rarer states have less data, but we still assume L\'evy stable distributions.
  \end{itemize}

@@

  % BJC2: I need to look into the motion when a solute is trapped. It should have a very low H.
  \noindent Motion within states is anticorrelated. 
  \begin{itemize}
    \item We calculated the self-similarity parameter for motion within each state.
  \end{itemize}

  \noindent The emissions resulting from transitions between states are anticorrelated.
  \begin{itemize}
    \item We simulated these emissions by combining all transition emissions into a single
    distribution with a single self-similarity parameter.
    \item We are unaware of techniques for simulating correlated draws from L\'evy distributions
    with varying shapes.
  \end{itemize}

  % BJC2: Could explore a second model with an emission distribution for transitions in tails versus pores.

  % BJC2: FIGURE: autocorrelation of motion while trapped in a state and autocorrelation of emissions.

  % BJC2: This figure will show predicted MSDs versus MD MSDs
  \begin{figure}[!h]
  \centering
  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
  \caption{}\label{fig:msd_MET}
  \end{figure}

%  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
%  \begin{itemize}
%    \item In general, we observe negative correlation between hops.
%    \item A L\'evy driven OU process may be a more appropriate way to model
%    the stochastic dynamics of this system since you can incorporate autocorrelation.
%    \item Extracting reliable correlation functions is difficult with our data
%    due to relatively frequent switching resulting in sets of short disjoint time 
%    series describing each state.
%    % \item Therefore we did not do this and attempted to fit a different model. 
%    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
%  \end{itemize}

  We projected the long timescale behavior using this model. 
  %BJC2: TABLE. 
  %BJC2: Would probably be best to combine this with table from anomalous diffusion.

@@

  % MRS1: will want to make a stateemnt about whether these approaches
  % are together good enough for predictive purposes, and if not,
  % explore what else should be done in the future.
  % BJC2: It seems like it would be hard to make say these can be used
  % for prediction without experimental confirmation of the trends that we observe.

  We have tested two different mathematical frameworks for describing solute
  motion in an H\textsubscript{II} phase LLC membrane.
  \begin{itemize}
    \item Subordinated fractional Brownian motion has a nice theoretical foundation
    in the anomalous diffusion literature. A two mode model that describes dynamics
    based on whether a solute is in or out of the pore region leads to MSDs fairly
    consistent with MD simulated trajectories.
    \item Markov state modeling with predefined states gives a nice description
    of transitions between observed states as well as the type of stochastic 
    behavior shown in each state. However, it doesn't accurately portray correlated
    time series behavior leading to overpredicted MSDs.
  \end{itemize}
